\section{Empirical Analysis}\label{sec:analysis}

%The nature of the randomized controlled experiment used to collect the dataset 
%of high service tier users allows us to evaluate the effect of a 
%\emph{factor}, the service plan upgrade, as a treatment applied to a control 
%group. 

Controlled experiments are difficult to do on the Internet scale. However, in 
our work, we had access to a randomized control experiment used to collect a 
dataset on the scale of a large city. This enables us to study the effect of 
just one factor, \emph{the service plan upgrade}, while controlling the affect 
of other factors, such as price, performance, or regional differences between 
users.

By concentrating in particular on a group of high service plan users, who were 
upgraded without their knowledge, we mitigate the affect of biases that 
previous studies on usage and capacity suffer from: (a) \emph{Avoid behavioral 
change bias:} offering users with high capacity a further increase without 
their knowledge avoids the risk of behavioral changes that may occur when one 
purposefully buys a higher bandwidth connection; and (b) \emph{Avoid 
dissatisfied user bias:} we study high capacity tier users in a \control{} 
group, that are are not utilizing their access link completely, and thereby 
mitigate the effect of traffic biases that occur because subscribers' previous 
capacity was insufficient for their usage. Studying datasets with these biases 
are prone to positive correlations between usage and capacity, which we 
avoid by examining a single high capacity tier with an unannounced upgrade.

\begin{table}[ht]
\small 
\begin{tabular}{| c | c |}\hline
\textbf{Parameter} & \textbf{Definition}	\\\hline
Demand per Subscriber& \(\frac{\text{aggregate bytes transferred in 
measurement interval}}{\text{number of contributing subscribers}}\)	\\
Prime Time		& 8:00 PM - 12:00 AM   		\\
Prime Time Ratio 	& \( \frac{ \text{avg usage in peak (prime-time) 
hour}}{ \text{avg usage in off-peak hour}}\) 		\\
Peak Period		& Time of demand 95\% of max    \\
Peak Ratio 		& \(\frac{\text{95\%-ile of max daily 
traffic demand}}{\text{mean of daily traffic demand}}\)	\\\hline
\end{tabular}
\caption{Evaluation Criteria}
\label{tab:eval-criteria}
\end{table}


\paragraph{Evaluation Criteria. } \todo{REDO this paragraph.} We describe daily 
traffic demand, 
prime-time ratio, and peak usage as criteria to evaluate general trends 
and changes in traffic demand (table~\ref{tab:eval-criteria}). We interpret the 
behavior of the datasets both separately as well as comparatively as (1) 
general inferences drawn from analyzing the dataset,  and (2) comparative 
inferences drawn from observing changes in user behavior due to the upgrade in 
access link bandwidth. We report on the results for uplink traffic 
demand where applicable. Lastly, we also evaluate the prevalence of the 
small number of subscribers who actively exceeded the service tier bandwidth 
they were paying for (105 Mbps) after the unannounced service tier upgrade to 
250 Mbps.

%\paragraph{Temporal Trends. } We aggregate the traffic demand over multiple 
%households during the same sample period, and present daily or weekly 
%description (mean, median, and 95th percentiles) as a time series.
%\paragraph{Spacial Trends. } We aggregate the traffic demand of a single 
%subscriber over its lifetime to measure their aggregated traffic demand, and 
%present description of aggregated subscribers (mean, median, and 95th 
%percentiles).

\input{behavior}

\input{peakratio}

\input{primetime}

\input{prevalence}