\section*{Appendices: FCC Issues of Inquiry}
\label{sec:appendix}

In the FCC report No. 14-113, released on Aug 5, 2014~\cite{fcc2014progress-report},
the Commission asks some relevant questions about broadband usage, and requests comments
from the community to improve its decision making process. The FCC report No. 15-10A1
answers some of these questions but raises issues for future progress reports.
We summarize their comments and questions with regards to usage behavior
as follows:
%\footnote{Note that the paragraph
%\# corresponds to the paragraph in the Eleventh Broadband Progress Report, FCC No. 
%15-10A1~\cite{fcc2015progress-report}\label{foot:fcc-issue-numbers}}

% comments for FCC:
% Can be mitigated by asking for usage instead from ISP first hop per household byte counters every 15 min. At least estimate usage (even if many apps in parallel) do they bottleneck or no?
% Why our comments are important:
%- measurement: understand the need for reco committee.
%- not biased (ATnT, verizon etc).
%- also understand broadband dynamics
%- important issues deserving our timely attention

\renewcommand{\thesubsection}{\Alph{subsection}}

\subsection{Tenth Broadband Progress Report}
\label{subsec:fcc2014}

Issues from the Tenth Broadband Progress Notice of Inquiry FCC 14-113, released 
August 5, 2014~\cite{fcc2014progress-report}

% purpose
\paragraph{3. Purpose of the Report. } We seek comment on the benchmarks we should use 
to define ``advanced telecommunications capability,'' explore whether we should establish 
separate benchmarks for fixed and mobile services, which data we should rely on in 
measuring broadband, whether and how we should take into account differences in 
broadband deployment, particularly between urban areas versus non-urban and Tribal 
areas, and other issues.
%We seek comment on whether we should modify the 4 megabits per second (Mbps) download and 1 Mbps upload (4 Mbps/1 Mbps) speed benchmark we have relied on in the past reports. We also seek comment on whether we should consider latency and data usage allowances as additional core characteristics of advanced telecommunications capability.

% speed and uses
\paragraph{6. Broadband Speed Benchmark.} Does service with speeds of 4 Mbps/1 Mbps 
provide consumers the ability to originate and receive these services? ... We seek 
comment on whether we should continue to benchmark broadband based on actual speeds, 
rather than advertised speeds, to the extent the two are different.

% peak usage time
% Peak usage is defined as the average data consumed between 7:00 to 11:00 pm on weeknights. The FCC asks if evaluating peak time usage is an efficient metric, or if average usage over a day should be considered instead.
\paragraph{13. Relying Upon Peak Usage Time.}
We seek comment on whether we should assess bandwidth requirements for a typical household
during peak Internet usage periods, from 7 pm to 11 pm on weeknights.
We seek comment on the types of broadband uses that are common, often used simultaneously, 
within a household during peak periods, and the appropriate bandwidth that would be 
necessary to accommodate those uses, to the extent that we determine that it is 
reasonable under section 706(b) to consider multiple simultaneous uses of broadband. 
We also seek comment on whether it is reasonable under the statute to set a speed 
benchmark on the basis of ``peak usage time.'' Is peak usage time an efficient metric? 
Should we instead consider the average household usage over a 24-hour period or over 
some other time period, or in some other manner entirely? We recognize that every 
household is unique, and that the services each household member uses will vary. We 
seek comment on whether establishing a reasonable household usage scenario during 
peak periods will assist the Commission in identifying a benchmark that is a 
necessary component of ``advanced telecommunications capability.''

% upload and download speeds needed at peak periods
\paragraph{15. Evaluating Downstream Usage during Peak Time.}
We seek comment on whether a download speed of 10 Mbps would adequately reflect
Congress’s goal of evaluating advanced telecommunications capability. Does 10 Mbps 
satisfy current demand, especially during peak time? Even assuming that it does, 
should the benchmark be higher than the minimum necessary to meet existing demand, 
i.e., should the benchmark be set to accommodate some level of anticipated future 
demand, particularly if the Commission does not intend to adjust the benchmark 
annually?... How should the Commission forecast future household broadband uses 
to justify such a benchmark?

\paragraph{17. Evaluating Upstream Usage.} We thus seek comment on whether a 1 Mbps 
upload speed is sufficient to meet the goals set forth in section 706. We also seek 
comment on whether there is a basis for the disparity between download and upload 
speeds in any speed threshold(s) used by the Commission. For example, if the Commission 
increases the download speed benchmark, should it also increase the upload speed benchmark?
Why or why not?

% Adoption based broadband benchmarking
\paragraph{18. Setting a Speed Benchmark Based on Adoption Rates.} We seek comment on 
whether the Commission should consider the rates at which consumers are adopting 
particular speeds when setting a speed benchmark. We seek comment on whether a higher 
benchmark is appropriate when the Fourth Measuring Broadband America Report indicates 
that consumers continue to migrate to higher broadband speeds.

% Taxonomy of users even in a single speed tier
\paragraph{19. Adoption of the Fastest Available Speed Tier} Should the benchmark be based 
on the fastest speed tier to which a substantial portion of
consumers subscribe? How should the Commission define ``substantial portion'' and how 
should we interpret such demand? Would using such a metric accurately reflect the market 
choices and needs of consumers based on the service offerings available to them? Does a 
particular adoption rate (to be determined) by consumers with access to broadband 
demonstrate that there is sufficient demand for that speed tier? Does adoption at a 
certain speed demonstrate or suggest that service of that speed is necessary to 
enable users to originate and receive high-quality voice, data, graphics, and video 
telecommunications?

% separate benchmarks: min broadband = 10/1, better broadband = 25/3, schools and libraries = 100...
%broadband requirements are not uniform throughout the nation. Some users will have significantly greater needs. The FCC is interested to know whether it should opt for multiple benchmarks depending on user scenario, usage, occupation, etc.? 
\paragraph{22. Multiple Speed Benchmarks.} We also seek comment on whether the Commission
should consider establishing multiple benchmarks. Multiple benchmarks could improve our ability
to assess whether advanced telecommunications capability is being deployed in a reasonable
and timely manner by recognizing that broadband requirements are not uniform throughout the 
nation. For example, while the ``typical use'' 10 Mbps download speed benchmark described 
above is intended to satisfy common household broadband demand, some users, such as larger 
families or teleworkers, will have significantly greater bandwidth needs. We seek comment 
on whether the Commission should adopt more than one speed benchmark and if so, how we 
should use the different benchmarks to evaluate whether deployment is occurring in a 
reasonable and timely manner.

% IMP: Usage as a Broadband Benchmark
\paragraph{27. Usage as a Broadband Benchmark.} The Commission has indicated that it might consider
data usage allowance as a core characteristic that affects what consumers can do with their broadband
service.
Should we include usage in our section 706 assessment? If so, how?
%We seek comment on what data usage allowances most broadband providers offer today, and the impact of these usage allowances on setting a benchmark. For example, do consumers routinely exceed the usage allowance for the service to which they subscribe and if so, is additional capacity available for an additional fee? If so, how frequently do consumers avail themselves of that option?

% how to measure the amount of data consumers use - form 477
\paragraph{29. Broadband Usage Threshold. } How would the Commission implement a broadband usage
threshold? Should the Commission focus on the amount of data that consumers actually use each month,
instead of what broadband providers typically offer? What information, reports, or other sources are
available to measure the amount of data consumers use monthly?
%In particular, are there any sources
%concerning usage that the Commission could use to assess which carriers meet or do not
%meet the usage threshold?

% How should deployment be measured
\paragraph{37. Improving Progress Reports. } We seek comment on ways to improve the Commission’s
annual broadband progress reports, such as incorporating new data sources or conducting our
analysis differently. Are there other ongoing efforts to collect broadband deployment or
availability data that were not available, or that we did not include, in prior reports? 
We seek input on whether there are any particular surveys or other reports that would be
particularly beneficial to our section 706 analysis.


\subsection{Eleventh Broadband Progress Report}
\label{subsec:fcc2015}

Issues from the Tenth Broadband Progress Report and Notice of Inquiry FCC 15-10A1,
released February 9, 2015~\cite{fcc2015progress-report}.

% why some people do not adopt broadband - motivation to study usage patterns
\paragraph{7. Impact of Broadband Adoption on Availability and Deployment.}
As part of our inquiry
into ``the availability of advanced telecommunications capability to all Americans,''
we also examine broadband adoption--some reasons why Americans choose not to adopt
broadband could reflect factors that are relevant to its ``availability,'' such as
price and quality. While we continue to see that adoption lags behind deployment
to a significant degree, at all speeds, we do not know precisely why.
%The recent 2014 NTIA Digital Nation Report found the top reason given for
%non-adoption was consumers simply not wanting broadband, and the second most
%cited reason was because it was too expensive.
%Americans with lower median incomes and where the poverty rate,
%rural population rate, and unemployment rate is higher tend to have lower
%broadband adoption rates. These facts raise questions about whether
%broadband is ``availab[le] . . . to all Americans'' as the statute requires,
%and we will continue to evaluate both how we can improve our analysis in future
%Reports and how the Commission can address the adoption gap.
Although we evaluate adoption separately from deployment and our determination
about whether broadband is being deployed in a reasonable and timely fashion stands
independently from our evaluation of broadband adoption, examining adoption is useful
both as an indicator of what Americans may consider to be needed and separately as
a stimulator for deployment.

% need to add usage patterns to this study
%\paragraph{10. }
%In addition, we expect to examine other factors of availability, including usage
%allowances and price, latency, whether service at the relevant speed is available
%on a consistent and reliable basis, and whether the network is secure. We expect
%to examine these factors in the next Inquiry and will seek out ways to improve our
%ability to evaluate them, relevant to both fixed and mobile services.

%deployment will occur only if people adopt and ISPs can make money off it => must study why all people don't adopt => study usage (bb not needed) vs price (bb too expensive).
%\paragraph{12. } As a consequence of our conclusion that advanced telecommunications
% capability is not being deployed to all Americans in a reasonable and timely fashion,
% section 706 mandates that the Commission ``take immediate action to accelerate
% deployment of such capability by removing barriers to infrastructure investment and
% by promoting competition in the telecommunications market.''

% multiple standards - why and why not
\paragraph{23. Multiple Benchmarks. } NCTA recommends that the Commission ``should use
multiple benchmarks
in performing its section 706 analysis rather than just one'' because doing so would ``better
reflect the multi-faceted nature of today’s broadband marketplace, which features a wide
variety of technologies and services that are able to cater to the varying needs of American
consumers.'' Others in the record disagree, stating, for example, that ``[t]here is
no substantive rationale provided to warrant having multiple standards. One standard sends
a clear and easily understood message to all parties.'' At this time we decline to use multiple 
benchmarks in this Report. We find that the single benchmark we use in this Report, which
relies on a higher speed benchmark than prior reports, is the appropriate means to allow us
to analyze whether advanced service is being deployed.

% speed factor
\paragraph{26. Redefined Speed Benchmark. } ... requires consumers to have access to actual
download (i.e., to the customer) speeds of at least 25 Mbps and actual upload (i.e., from 
the customer) speeds of at least 3 Mbps (25 Mbps/3 Mbps). For schools and classrooms, we use
the same benchmark that the Commission already established for schools and classrooms of a 
short term benchmark of 100 Mbps per 1,000 students and staff and a long-term speed 
benchmark of 1 Gbps per 1,000 students and staff.

% consumers adopt higher speeds when they have the option
\paragraph{41. Consumer Needs affect Broadband Adoption. } Our own assessment of
consumers’ likely needs is confirmed by examining broadband
adoption. When speeds of 25 Mbps/3 Mbps are available, a substantial 
and fast-growing number of consumers are adopting and migrating to 
higher speeds. Examining the adoption trends from December 2011 to 
December 2013, we find that the adoption rate of this service or 
higher quadrupled. Customers are deciding for themselves at a very 
rapid rate that they need services at this or higher speeds

% household level rather than user level granularity
\paragraph{47. Consider Broadband at the Household Level. }
Because consumers usually purchase fixed broadband service for the household, and because the 
deployment data represent households rather than individuals, we find it reasonable to consider 
broadband needs at a household level, rather than what each individual household member, individually, 
may need.

% why single benchmarks might not work - there are many types of users within the same tier
%\paragraph{52. }
%Some commenters urge us to retain the 4 Mbps/1 Mbps benchmark228 or increase the
%benchmark to 10 Mbps/1 Mbps. ATnT asserts that section 706(b) is not ``myopically'' focused on the 
%subset of consumers who are the heaviest users.230 We agree. Section 706(b) is not ``myopically'' 
%focused on any particular subset of consumers. But it does require the Commission to assess deployment 
%of advanced services that are capable of performing specific functions, and doing so at a high 
%quality.

% availability and deployment
%\paragraph{64. }
%We affirm the Commission’s prior findings that, for the purpose of our analysis, the 
%terms broadband ``deployment'' and ``availability'' are broader than mere physical 
%presence of broadband networks. This interpretation is the most natural reading of
%section 706(b). Moreover, section 706 requires the Commission to conduct an inquiry
%into broadband ``availability'' and determine whether broadband ``is being deployed''
%in a reasonable and timely fashion. The statute does not indicate that a determination
%about whether broadband is being deployed must consider a set of circumstances narrower
%than the ``availability'' inquiry. We continue to interpret ``all Americans'' as establishing
%the goal of universal broadband availability for every American. As such, our annual
%determination as to how broadband ‘‘is being deployed’’ is simply an assessment of how
%well we are progressing toward the goal of ``availability to all Americans.''

% Factors influencing adoption: availability, price, quality, ...
\paragraph{65. Assessing Availability and Deployment.} We conclude that in determining
whether broadband is ``being deployed to all Americans in a reasonable and timely fashion,''
we must look at a variety of factors that affect access to broadband. ... Accordingly, as
in prior Reports, our inquiry includes an assessment of a variety of factors indicative of
broadband availability, such as price, quality, and adoption by consumers, as well as
physical network deployment.

%VI. REMOVING BARRIERS & PROMOTING COMPETITION 141.
\paragraph{141. Removing Barriers to Promote Competition. }
%In light of our finding that advanced telecommunications capability is not being deployed to all Americans in a reasonable and timely manner, the Commission must ''take immediate action to accelerate deployment of such capability by removing barriers to infrastructure investment and by promoting competition in the telecommunications market.'' In the last two Reports, the Commission found numerous barriers to infrastructure investment. In particular, the high costs associated with deploying and operating a broadband network coupled with low broadband adoption rates, present barriers.
As we have done in the past, we will continue to work on removing barriers to infrastructure
investment by identifying and helping to reduce potential obstacles to deployment, 
competition, and adoption -- concepts that we continue to recognize are tightly linked.

%usage of broadband is a barrier to deployment of higher speeds.
% measure usage of areas with no deployment (open data) - if it seems aggressive for a certain percentage of total people in that are => cost price analysis to deploy bb there. (almost the same as comcast's requirement to get at least 10 signatures in rural areas)
\paragraph{142. Barriers to Deployment and Adoption. } Because providers will consider
adoption rates when determining whether to build out facilities and offer service 
a particular area, we consider barriers to adoption as well as deployment. The 
key barriers to deployment and adoption include: (1) costs and delays in building 
out networks; (2) broadband service quality; (3) lack of affordable broadband 
Internet access services; (4) lack of access to devices and other broadband-capable
equipment; and (5) barriers to entry by potential competitors and, consequently, 
lack of competitive choice for consumers.
%only way is to show provider that on aggregate the deployment will be revenue generating => usage patterns to show that lower tiers are not satisfactory
%but we can't do this with current data unless comcast gives us low tier data!